Topic Scores

### 2019-02-20 Topic Scores.Rmd
deletes empty lines
simplifying key words

##Selectig keywords
```{r}
top_kw <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(3, beta) %>%
  pull(term)

kw <- unique(top_kw)

kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl",
    #unsure:
               "theory", "search", "perspective"
                )
kw <- setdiff(kw, kw_stopwords)
```

>>>>

##Selectig keywords
```{r}
top_words <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(3, beta) %>%
  pull(term)%>%
  unique

kw_stopwords =c(
  "student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue",
  "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford",
  "cuss", "lecture", "pbl",
    #unsure:
  "theory", "search", "perspective"
                )
kw <- setdiff(top_words, kw_stopwords)
```
